---
title: "Gunshots and Turf Wars:"
subtitle: Inferring Gang Territories from Administrative Data
date: "24 March 2020"
author: Brendan Cooley | Noam Reich
position: Ph.D. Candidates
institution: Princeton University
email: "bcooley (at) princeton.edu | noamg (at) princeton.edu"
note: These slides available at brendancooley.com/gangs

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "other/chi_aerial.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    fig_caption: true
    reveal_options:
      slideNumber: false
      progress: false
      controls: true
---


```{r references, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

# NOTE: loading knitr or kableExtra later in the slides seems to mess with revealjs
if (file.exists('references.RData')) load('references.RData')

```

```{r, child = "07_slides/introduction.rmd"}
```

```{r, child = "07_slides/data.rmd"}
```

```{r, child = "07_slides/model.rmd"}
```

```{r, child = "07_slides/estimation.rmd"}
```

```{r, child = "07_slides/results.rmd"}
```

# Conclusion

<div class="fragment">

**Limitations**

- Collapse dynamic process of border adjustment into static representation [@Bruhn2019]
- Detects largest gangs in Chicago but is unable to capture richness of gang network

</div>
<div class="fragment">

**Extensions**

- Extend to other cities
  + Data is available for all large municipalities
- Build cross section of gang maps across United States and elsewhere(?)
  + Characterize measurement error explicitly
- Building block for substantive research on gangs, violence, poverty, and policing

</div>

# Thank You  {.aligncenter}

# Table of Contents {id="toc"}

<div id="left">

**Sections**

1. <a href="#/introduction">Introduction</a>
2. <a href="#/data">Data</a>
3. <a href="#/model">Model</a>
4. <a href="#/estimation">Estimation</a>
5. <a href="#/results">Results</a>
</div>

<div id="right">

**Appendix**

1. <a href="#/chen">Number of Groups</a>
2. <a href="#/chen">Eigengaps</a>
3. <a href="#/cpd_match_table">Match Frequencies</a>
</div>

```{r, child = "07_slides/appendix.rmd"}
```

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />
