---
title: "Gunshots and Turf Wars:"
subtitle: Inferring Gang Territories from Administrative Data
date: "24 March 2020"
author: Brendan Cooley | Noam Reich
position: Ph.D. Candidates
institution: Princeton University
email: "bcooley (at) princeton.edu | noamg (at) princeton.edu"

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "other/chi_aerial.jpg"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    fig_caption: true
    reveal_options:
      slideNumber: false
      progress: false
      controls: true
---


```{r references, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

if (file.exists('references.RData')) load('references.RData')

```

```{r, child = "07_slides/introduction.rmd"}
```

```{r, child = "07_slides/data.rmd"}
```

```{r, child = "07_slides/model.rmd"}
```

```{r, child = "07_slides/estimation.rmd"}
```

# Thank You  {.aligncenter}

# Table of Contents {id="toc"}

fill this in

```{r, child = "07_slides/appendix.rmd"}
```





# Results

- `r K` gangs detected

<!-- ```{r scree, echo=FALSE, warning=FALSE, message=FALSE, fig.height=4.5, dpi=300}

screePlot

``` -->

## Empirical Covariances

<!-- ```{r emp_cov, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

block_hm

``` -->

## Territorial Partition

<!-- ```{r partition, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

chi_clusters_map

``` -->

## Conflict Intensities

<!-- ```{r b_hat, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

Bhat_hm

``` -->

# Next Steps

- Validation
  + Calculate empirical loss relative to Chicago gang map
- Uncertainty
  + Bootstrap tract-months, calculate confidence metrics for partition function, intervals for number of groups
- Robustness
  + Different levels of resolution, block groups? 
- Extend to other cities

