```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

source("../01_code/00_params.R")

```

# Gunshots and Turf Wars

<div class="fragment">

**Gunshots**

> "In 2006 nearly **50 percent of the homicides** and a large percentage of other violent crimes and property crimes committed in Chicago **were attributed to street gangs** that are involved in drug trafficking"
> 
> - @NDIC2007

- Inter- and intra-gang conflict in gang ethnographies
  + @Sanchez1991, @Decker1996, @Levitt2000, @Papachristos2009
- Not unique to Chicago
  + @Howell2018

</div>
<div class="fragment">

**Turf Wars**

> "Gang violence is often sparked by competitive relations over **turf.** A gang's turf has **economic and symbolic value**: the gang regulates who sells what on its street corners, and gang members take pride in controlling the blocks where they grew up. **Encroaching on another gang's turf can trigger violence** and a series of retaliations as gang members avenge fallen comrades." 
> 
> - @Vargas2016, *Wounded City*

- Territorial rent-seeking: racketerring, drug-selling monopolies, smuggling 
  + @Thrasher1927, @Sanchez1991, @Levitt2000, @Venkatesh2000
- Conflict over rent streams and challenges to reputations
  + @Brantingham2012, @Papachristos2013, @Vargas2016, @Ebdm2018

</div>

## Measurement Problem

- **Proposition:** understanding gunshots requires understanding gangs 
- **Problem:** gangs are covert organizations $\implies$ knowledge of gangs remains anecdotal and spatially circumscribed

. . .

**First-Order Descriptive Questions** 

1. How many gangs operate within a given municipality?
2. How is territory divided amongst them?

. . . 

**Existing Approaches**

- Police Records: @Bruhn2019 (Chicago), @Melnikov2019 (San Salvador)
  + Not broadly available or not shared with public
  + Reporting biases and auditability: how are data constructed?
- Newspapers, NLP, Mixed Methods [@Blattman2019; @Sobrino2019; @Signoret2020]
  + Require deep subject matter expertise, difficult to generalize beyond target locale

## Approach

**Observables:** Time-stamped, geolocated homicides and nonfatal shootings

- Widely available in administrative records on crime

**Unobservables:**

1. Number of gangs
2. Territorial partition

. . .

**Inferential Strategy**

1. Model data-generating process for shootings
    + Non-gang
    + Intra-gang
    + Inter-gang

. . .

2. Derive relationship between spatial covariance in shootings and unobservables
    + Generalization of @Trebbi2019 to inter-group conflict
    + Akin to stochastic block model (SBM) [@Holland1983]

. . .

3. Estimate model using observed spatial covariances
    + Spectral clustering [@Luxberg2007; @Lei2015; @Chen2018]

. . .

4. Validate results using **Chicago** Police Department (CPD) gang maps [@Bruhn2019]
    + Match partition function labels to those of CPD

## Bottom Line

```{r, echo=FALSE, warning=FALSE, message=FALSE, dpi=400, fig.height=5.5, fig.align="left"}

source("../05_figs/clusters.R")
tmap_arrange(chi_turf_binary_map, chi_outline_map)

```

## Bottom Line

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=400}

source("../05_figs/clusters.R")
comparison_maps

```