```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

libs <- c("tidyverse", "knitr", "patchwork")
ipak(libs)

J <- read_csv(J_path, col_names=FALSE) %>% pull(.)
K <- J - 1

J_all <- read_csv(J_all_path, col_names=FALSE) %>% pull(.)
K_all <- J_all - 1
K_all <- K_all %>% sort()

K_lower <- K_all[3]
K_upper <- K_all[97]

label_counts <- read_csv(label_counts_path) %>% filter(owner != "peaceful") %>% arrange(desc(count))
label_counts$count <- label_counts$count / L
colnames(label_counts) <- c("Gang", "Proportion")
label_counts$Gang <- stri_trans_totitle(label_counts$Gang)

LK_freq <- label_counts %>% filter(Gang=="Latin Kings") %>% pull(Proportion)
TS_freq <- label_counts %>% filter(Gang=="Two-Six") %>% pull(Proportion)

gang_frac_vec <- read_csv(gang_frac_path, col_names=FALSE) %>% pull()
gang_frac_ci <- quantile(gang_frac_vec, c(.025, .975))

sample_agreement_ratio <- read_csv(sample_agreement_ratio_path, col_names=FALSE) %>% pull()
cpd_agreement_ratio <- read_csv(cpd_agreement_ratio_path, col_names=FALSE) %>% pull()
cpd_agreement_ratio_peaceful <- read_csv(cpd_agreement_ratio_peaceful_path, col_names=FALSE) %>% pull()
cpd_agreement_ratio_gang <- read_csv(cpd_agreement_ratio_gang_path, col_names=FALSE) %>% pull()

cpd_agreement_ratio_ci <- quantile(cpd_agreement_ratio, c(.025, .975))
cpd_agreement_ratio_peaceful_ci <- quantile(cpd_agreement_ratio_peaceful, c(.025, .975))
cpd_agreement_ratio_gang_ci <- quantile(cpd_agreement_ratio_gang, c(.025, .975))

```

# Results {id="results"}

<div class="fragment">

**Number of Gangs**

- `r K_lower`-`r K_upper` gangs detected
- `r cpd_gangs_N` gangs own at least one tract according to CPD, but three largest gangs we detect occupy `r round(gd_vl_bps_area / all_area*100, 1)` of all gang turf
- <a href="#/eigengaps">Eigengaps</a>

</div>
<div class="fragment">

**Territorial Partition**

- Paritition labels matched to those of Gangster Disciples, Vice Lords, and Black P Stones with highest frequency
- `r round(gang_frac_ci[1]*100, 0)`-`r round(gang_frac_ci[2]*100, 0)` percent of census tracts are gang-occupied
- `r round(cpd_agreement_ratio_ci[1]*100, 0)`-`r round(cpd_agreement_ratio_ci[2]*100, 0)` percent of our labels agree with those of CPD
	+ **Baseline:** `r round(sample_agreement_ratio*100, 0)` percent of CPD labels agree with random label permutations
- <a href="#/cpd_match_table">Match Frequencies</a>

</div>

## Empirical Covariances

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

source("../05_figs/P.R")
P_hm + plot_spacer()

```

## Empirical Covariances

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

source("../05_figs/P.R")
block_hm

```

## Territorial Partition

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

source("../05_figs/clusters.R")
comparison_maps

```

## Conflict Intensities

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

source("../05_figs/Bhat.R")
Bhat_hm

```

## Conflict Intensities

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

Bhat_ci

```

